Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm_regret.tex
cleaned up formulas, proof

\begin{extraproof}{Theorem~\ref{rst:regret}}
Regret can arise in two ways:
(1) an agent was incentivized to pull a suboptimal arm, or
(2) an agent myopically pulled a suboptimal arm.
By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
incentivizes agents at most 
$O\left( N\exp\left(\frac{2}{p}\right) \right)$
times in expectation, each time causing regret at most \MAXR,
for a total expected regret of at most
$O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)$.
For the rest of the proof, we focus on the regret incurred when agents
pull arms myopically and make mistakes.

@@

\begin{align*}
\lefteqn{
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
\\ & = 
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \Diam^2 d^2 \sigma^2 \cdot \log^3(T) \right).
\end{align*}
\end{extraproof}

>>>>

\begin{emptyextraproof}{Theorem~\ref{rst:regret}}
Regret can arise in two ways:
(1) an agent was incentivized to pull a suboptimal arm, or
(2) an agent myopically pulled a suboptimal arm.
By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
incentivizes agents at most 
$O\left( N\exp\left(\frac{2}{p}\right) \right)$
times in expectation, each time causing regret at most \MAXR,
for a total expected regret of at most
$O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)$.
For the rest of the proof, we focus on the regret incurred when agents
pull arms myopically and make mistakes.

@@

\begin{align*}
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)
& = 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right).\QED
\end{align*}
\end{emptyextraproof}
